Probability

### 2016-04-25 prob.tex
prob.tex Add a corollary, and a little bit proof...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}

@@

Naturally, we may ask: is every probability measure induced from a
state by the Born rule? The answer is yes by Gleason's theorem when
the dimension~$\ge3$ and extend the domain of the Born rule to mixed
state~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\ffzd}[1]{{\mathbb{F}^{d\;*}_{#1}}}
\def\C{{\mathbb{C}}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}
\newcommand{\melement}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\expect}[2]{ \langle #1 | #2 | #1 \rangle}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}
\theoremstyle{plain}
\newtheorem{thm}{\protect\theoremname}
\theoremstyle{plain}
\newtheorem{cor}[thm]{Corollary}

@@

Naturally, we may ask: is every probability measure induced from a
state by the Born rule? The answer is yes by Gleason's theorem when
the dimension~$\ge3$~\cite{gleason1957,peres1995quantum,Redhead1987-REDINA}.
Furthermore, a simple corollary of Gleason's theorem can show the
Born rule is the unique function satisfying conditions 1. to 3.
\begin{cor}
The Born rule is the unique function satisfying conditions 1. to 3.
\end{cor}
\begin{proof}
Assume there is another function $\tilde{\mu}'$ such that $\tilde{\mu}'_{\rho}$
is a quantum probability measure for all mixed state~$\rho$. We
are going to prove $\tilde{\mu}'=\tilde{\mu}$.

Fix a pure normalized state $\phi$, $\tilde{\mu}'_{\phi}$ is a quantum
probability measure by condition 2. By Gleason's theorem, there is
a mixed state ~$\rho'$, such that $\tilde{\mu}'_{\phi}\left(E\right)=\Tr\left(\rho'E\right)=\sum_{j=1}^{N}q_{j}\tilde{\mu}_{\psi_{j}}\left(E\right)$
for all event $E$.

Consider the event $E'=\mathbb{1}-\proj{\phi}$, we have 
\begin{eqnarray*}
0 & \overset{\textrm{Condition 3}}{=} & \tilde{\mu}_{\phi}\left(E'\right)\\
 & = & \sum_{j=1}^{N}q_{j}\tilde{\mu}_{\psi_{j}}\left(E'\right)
\end{eqnarray*}
Because $q_{j}>0$, we have $\tilde{\mu}_{\psi_{j}}\left(E\right)=0$,
i.e., $\psi_{j}$ is orthogonal to a co-dimension-$1$ subspace $E'$.
However, the only subspace orthogonal to $E'$ is span by $\ket{\phi}$.
Hence, $\tilde{\mu}'_{\phi}=\tilde{\mu}_{\phi}$.
\end{proof}
